Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-14 paper.qmd
Updated the projections for five Gaussian clusters

five_gau_proj_tsne_model <- gen_proj_langevitour(
  points_df = df_exe,
  projection = projection,
  edge_df = distance_df_small_edges |> select(-distance)
) +
  xlim(c(-0.18, 0.1)) +
  ylim(c(-0.78, -0.55))
```

@@

five_gau_proj_umap_model <- gen_proj_langevitour(
  points_df = df_exe,
  projection = projection,
  edge_df = distance_df_small_edges |> select(-distance)
) +
  xlim(c(-0.18, 0.1)) +
  ylim(c(-0.78, -0.55))
```

@@

five_gau_proj_pacmap_model <- gen_proj_langevitour(
  points_df = df_exe,
  projection = projection,
  edge_df = distance_df_small_edges |> select(-distance)
) +
  xlim(c(-0.18, 0.1)) +
  ylim(c(-0.78, -0.55))
```

>>>>

points_only_df <- df_exe |>
    dplyr::select(-type)

projected <- as.matrix(points_only_df) %*% projection

projected_df <- projected |>
  tibble::as_tibble(.name_repair = "unique") |>
  dplyr::rename(c("proj1" = "...1",
                  "proj2" = "...2")) |>
  dplyr::mutate(type = df_exe$type) |>
  dplyr::mutate(ID = dplyr::row_number())

proj_model <- projected_df |>
  dplyr::filter(type == "model")

model_df <- dplyr::left_join(
  distance_df_small_edges |> select(-distance), 
  proj_model, 
  by = c("from" = "ID"))

names(model_df)[3:NCOL(model_df)] <- paste0(names(proj_model)[-NCOL(proj_model)], "_from")

model_df <- dplyr::left_join(model_df, proj_model, by = c("to" = "ID"))
names(model_df)[(2 + NCOL(proj_model)):NCOL(model_df)] <- paste0(names(proj_model)[-NCOL(proj_model)], "_to")

five_gau_proj_tsne_model <- projected_df |>
  filter(type == "data") |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        alpha = 0.3) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  xlim(c(-0.18, 0.1)) +
  ylim(c(-0.78, -0.55))

# five_gau_proj_tsne_model <- gen_proj_langevitour(
#   points_df = df_exe,
#   projection = projection,
#   edge_df = distance_df_small_edges |> select(-distance)
# ) +
#   xlim(c(-0.18, 0.1)) +
#   ylim(c(-0.78, -0.55))
```

@@

points_only_df <- df_exe |>
    dplyr::select(-type)

projected <- as.matrix(points_only_df) %*% projection

projected_df <- projected |>
  tibble::as_tibble(.name_repair = "unique") |>
  dplyr::rename(c("proj1" = "...1",
                  "proj2" = "...2")) |>
  dplyr::mutate(type = df_exe$type) |>
  dplyr::mutate(ID = dplyr::row_number())

proj_model <- projected_df |>
  dplyr::filter(type == "model")

model_df <- dplyr::left_join(
  distance_df_small_edges |> select(-distance), 
  proj_model, 
  by = c("from" = "ID"))

names(model_df)[3:NCOL(model_df)] <- paste0(names(proj_model)[-NCOL(proj_model)], "_from")

model_df <- dplyr::left_join(model_df, proj_model, by = c("to" = "ID"))
names(model_df)[(2 + NCOL(proj_model)):NCOL(model_df)] <- paste0(names(proj_model)[-NCOL(proj_model)], "_to")

five_gau_proj_umap_model <- projected_df |>
  filter(type == "data") |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        alpha = 0.3) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  xlim(c(-0.18, 0.1)) +
  ylim(c(-0.78, -0.55))

# five_gau_proj_umap_model <- gen_proj_langevitour(
#   points_df = df_exe,
#   projection = projection,
#   edge_df = distance_df_small_edges |> select(-distance)
# ) +
#   xlim(c(-0.18, 0.1)) +
#   ylim(c(-0.78, -0.55))
```

@@

points_only_df <- df_exe |>
    dplyr::select(-type)

projected <- as.matrix(points_only_df) %*% projection

projected_df <- projected |>
  tibble::as_tibble(.name_repair = "unique") |>
  dplyr::rename(c("proj1" = "...1",
                  "proj2" = "...2")) |>
  dplyr::mutate(type = df_exe$type) |>
  dplyr::mutate(ID = dplyr::row_number())

proj_model <- projected_df |>
  dplyr::filter(type == "model")

model_df <- dplyr::left_join(
  distance_df_small_edges |> select(-distance), 
  proj_model, 
  by = c("from" = "ID"))

names(model_df)[3:NCOL(model_df)] <- paste0(names(proj_model)[-NCOL(proj_model)], "_from")

model_df <- dplyr::left_join(model_df, proj_model, by = c("to" = "ID"))
names(model_df)[(2 + NCOL(proj_model)):NCOL(model_df)] <- paste0(names(proj_model)[-NCOL(proj_model)], "_to")

five_gau_proj_pacmap_model <- projected_df |>
  filter(type == "data") |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        alpha = 0.3) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  xlim(c(-0.18, 0.1)) +
  ylim(c(-0.78, -0.55))

# five_gau_proj_pacmap_model <- gen_proj_langevitour(
#   points_df = df_exe,
#   projection = projection,
#   edge_df = distance_df_small_edges |> select(-distance)
# ) +
#   xlim(c(-0.18, 0.1)) +
#   ylim(c(-0.78, -0.55))
```
